---
title: "Data Extraction"
output: html_notebook
---


Table of Contents:

1. Data Collection
1.1 Tweet Collection
1.2 Data Export
2. Data Transformation
2.1 Data Loading
2.2 Cleaning Data
2.3 Sentiment Analysis
2.4 Topic Modelling
2.4.1 LDA Topic Modelling
2.4.2 STM Topic Modelling
2.5 Additional Analysis
2.6 Data Export
3. Data Visualisation
3.1 Data Loading
3.2 Generating visuals
3.3 Sentiment visuals
3.4 Topic Modelling visuals
3.4.1 Latent Dirichlet Allocation 
3.4.2 Structural Topic Modelling
3.5 Additional visuals




# 1. Data Collection

```{r message=FALSE, warning=FALSE, include=FALSE}
#install_github("mkearney/rtweet")

#Packages
library(usethis)
library(devtools)
library(rtweet)
library(readr)
library(topicmodels)
library(maps)
```

## 1.1 Tweet Collection

### Checking rate limits
```{r}
# see rate limits
# The rate limit for the standard search API is 18,000 tweets per fifteen minutes. With a bearer token, the rate limit is 45,000 tweets per fifteen minutes. 
rate_limits<-rate_limit()
head(rate_limits[,1:4])
```


### Collect first batch of tweets
```{r echo=TRUE, message=TRUE, warning=TRUE}
#PULL FINAL VERSION ON MONDAY OR TUESDAY
News24_tweets <- get_timelines(c("News24"), n = 3200, include_rts=FALSE)
TimesLIVE_tweets <- get_timelines(c("TimesLIVE"), n = 3200, include_rts=FALSE)
eNCA_tweets <- get_timelines(c("eNCA"), n = 3200, include_rts=FALSE)

```


### Collect second batch of tweets
```{r echo=TRUE, message=TRUE, warning=TRUE}
IOL_tweets <- get_timelines(c("IOL"), n=3200, include_rts=FALSE)
SABCNews_tweets <- get_timelines(c("SABCNews"), n=3200, include_rts=FALSE)
ewnupdates_tweets <- get_timelines(c("ewnupdates"), n=3200, include_rts=FALSE)
```

### Collecting additional tweets
```{r}
#Not used
SAgovnews_tweets <- get_timelines(c("SAgovnews"), n=3200, include_rts=FALSE)
SowetanLIVE_tweets <- get_timelines(c("SowetanLIVE"), n=3200, include_rts=FALSE)
City_Press_tweets <- get_timelines(c("City_Press"), n=3200, include_rts=FALSE)
mailandguardian_tweets <- get_timelines(c("mailandguardian"), n=3200, include_rts=FALSE)
```


### Collect third batch of tweets

```{r echo=TRUE, message=FALSE, warning=FALSE}
#Not used
trend_tweets <- get_trends("South Africa")
```

### Collect fourth batch of tweets

```{r}
#Define terms to search by
q1 <- "Covid OR Corona OR Covid-19 OR Covid19 OR Coronavirus OR SARS-CoV-2 OR SARS-CoV"
q2 <- "OR #Covid OR #Corona OR #Covid-19 OR #Covid19 OR #Coronavirus OR #SARS-CoV-2 OR #SARS-CoV"
q <- paste(q1,q2)

#UPDATE DAILY
#Collecting tweets for South Africa
tweets_za_22 <- search_tweets(q,geocode = lookup_coords("South Africa"), since="2020-06-22", until="2020-06-23", type="recent", include_rts=FALSE, n=18000)

#Collecting tweets for largest city in each province
tweets_bloem_22 <- search_tweets(q,geocode = lookup_coords("Bloemfontein"), since="2020-06-22", until="2020-06-23", type="recent", include_rts=FALSE, n=18000)
tweets_cpt_22 <- search_tweets(q,geocode = lookup_coords("Cape Town"), since="2020-06-22", until="2020-06-23", type="recent", include_rts=FALSE, n=18000)
tweets_durb_22 <- search_tweets(q,geocode = lookup_coords("Durban"), since="2020-06-22", until="2020-06-23", type="recent", include_rts=FALSE, n=18000)
tweets_jhb_22 <- search_tweets(q,geocode = lookup_coords("Johannesburg"), since="2020-06-22", until="2020-06-23", type="recent", include_rts=FALSE, n=18000)
tweets_kim_22 <- search_tweets(q,geocode = lookup_coords("Kimberley"), since="2020-06-22", until="2020-06-23", type="recent", include_rts=FALSE, n=18000)
tweets_klerk_22 <- search_tweets(q,geocode = lookup_coords("Klerksdorp"), since="2020-06-22", until="2020-06-23", type="recent", include_rts=FALSE, n=18000)
tweets_mbomb_22 <- search_tweets(q,geocode = lookup_coords("Mbombela"), since="2020-06-22", until="2020-06-23", type="recent", include_rts=FALSE, n=18000)
tweets_polo_22 <- search_tweets(q,geocode = lookup_coords("Polokwane"), since="2020-06-22", until="2020-06-23", type="recent", include_rts=FALSE, n=18000)
tweets_pe_22 <- search_tweets(q,geocode = lookup_coords("Port Elizabeth"), since="2020-06-22", until="2020-06-23", type="recent", include_rts=FALSE, n=18000)
```


### Collect fifth batch of tweets

```{r}
#Retrieve profiles
News24_profile <- lookup_users("News24")
TimesLIVE_profile <- lookup_users("TimesLIVE")
eNCA_profile <- lookup_users("eNCA")
IOL_profile <- lookup_users("IOL")
SABCNews_profile <- lookup_users("SABCNews")
ewnupdates_profile <- lookup_users("ewnupdates")

#Get Followers count
News24_followers <- News24_profile$followers_count
TimesLIVE_followers <- TimesLIVE_profile$followers_count
eNCA_followers <- eNCA_profile$followers_count
IOL_followers <- IOL_profile$followers_count
SABCNews_followers <- SABCNews_profile$followers_count
ewnupdates_followrtd <- ewnupdates_profile$followers_count

#Get Friends count
News24_followers <- News24_profile$friends_count
TimesLIVE_followers <- TimesLIVE_profile$friends_count
eNCA_followers <- eNCA_profile$friends_count
IOL_followers <- IOL_profile$friends_count
SABCNews_followers <- SABCNews_profile$friends_count
ewnupdates_followers <- ewnupdates_profile$friends_count
```




## 1.2 Data Export
```{r}
#UPDATE DAILY
#Export Filtered Data for 21/06/2020
write_rds(tweets_za_22, "Data/Raw_Filtered_Data/tweets_za_22.rds")
write_rds(tweets_bloem_22, "Data/Raw_Filtered_Data/tweets_bloem_22.rds")
write_rds(tweets_cpt_22, "Data/Raw_Filtered_Data/tweets_cpt_22.rds")
write_rds(tweets_durb_22, "Data/Raw_Filtered_Data/tweets_durb_22.rds")
write_rds(tweets_jhb_22, "Data/Raw_Filtered_Data/tweets_jhb_22.rds")
write_rds(tweets_kim_22, "Data/Raw_Filtered_Data/tweets_kim_22.rds")
write_rds(tweets_klerk_22, "Data/Raw_Filtered_Data/tweets_klerk_22.rds")
write_rds(tweets_mbomb_22, "Data/Raw_Filtered_Data/tweets_mbomb_22.rds")
write_rds(tweets_polo_22, "Data/Raw_Filtered_Data/tweets_polo_22.rds")
write_rds(tweets_pe_22, "Data/Raw_Filtered_Data/tweets_pe_22.rds")

```


```{r echo=TRUE}
# Exporting Timeline Data
write_rds(News24_tweets, "Data/Raw_Timeline_Data/News24_tweets.rds")
write_rds(TimesLIVE_tweets, "Data/Raw_Timeline_Data/TimesLIVE_tweets.rds")
write_rds(eNCA_tweets, "Data/Raw_Timeline_Data/eNCA_tweets.rds")
write_rds(IOL_tweets,"Data/Raw_Timeline_Data/IOL_tweets.rds")
write_rds(SABCNews_tweets,"Data/Raw_Timeline_Data/SABCNews_tweets.rds")
write_rds(ewnupdates_tweets,"Data/Raw_Timeline_Data/ewnupdates_tweets.rds")
write_rds(SAgovnews_tweets,"Data/Raw_Timeline_Data/SAgovnews.rds")
write_rds(SowetanLIVE_tweets,"Data/Raw_Timeline_Data/SowetanLIVE.rds")
write_rds(City_Press_tweets,"Data/Raw_Timeline_Data/City_Press.rds")
write_rds(mailandguardian_tweets,"Data/Raw_Timeline_Data/mailandguardian.rds")
```

```{r}
#Exporting followers and following counts

```

